---
title: "Cases"
author: "Jens Hesel"
date: "18 mar 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Packages
```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(readr)
```

Loads data
```{r}
vital_sign_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/vital_sign_final.csv")
```

The random patient
```{r}
vital_sign_sample %>%
  filter(encounterId==1111) -> random
```

Shows the four vital signs
```{r}
random %>%
  distinct(time, rr, pr, mBP, spO2) -> random
```

Plots the random patients vital signs
```{r}
random$pr <- as.numeric(as.character(test$pr))
random$rr <- as.numeric(as.character(test$rr))
random$spO2 <- as.numeric(as.character(test$spO2))

#Plotter rr ift tiden 
ggplot(data=random, aes(x=time, y=value, color=variable)) + 
  geom_line(aes(y=pr, col="PR")) +
  geom_line(aes(y=rr, col="RR")) +
  geom_line(aes(y=spO2, col="spO2"))
```


Case 1 - Many measurements
```{r}
vital_sign_sample %>%
  filter(encounterId==1111) -> grouped_data1

grouped_data1$pr <- as.numeric(as.character(grouped_data1$pr))
grouped_data1$rr <- as.numeric(as.character(grouped_data1$rr))
grouped_data1$mBP <- as.numeric(as.character(grouped_data1$mBP))
grouped_data1$spO2 <- as.numeric(as.character(grouped_data1$spO2))


ggplot(data=grouped_data1, aes(x=time, y=value, color=variable)) + 
  geom_line(aes(y=pr, col="rr")) +
  geom_line(aes(y=rr, col="pr")) +
  geom_line(aes(y=spO2, col="spO2"))

```


The Patient arrived at:
```{r}
arrival_time1 <- encounter_sample$arrivalTime[encounter_sample$encounter_id==1111]
arrival_time1 <- na.omit(arrival_time)
arrival_time1
```


The patient was discharged at:
```{r}
discharge_time1 <- encounter_sample$discharge_time[encounter_sample$encounter_id==1111]
discharge_time1 <- na.omit(discharge_time)
discharge_time1
```


The patient was amitted for a total time of:
```{r}
difftime(discharge_time1, arrival_time1)
```


The patient have the total number of measurements
```{r}
grouped_data1 %>%
  group_by(encounterId) %>%
  mutate(number_of_measures=n()) -> grouped_data1
  
#Isolerer patient ID og tilhørende antal målinger
grouped_data1 %>%
  distinct(encounterId, number_of_measures) %>%
  arrange(desc(number_of_measures)) -> grouped_data1

grouped_data1$number_of_measures[grouped_data1$encounterId==53104884]
```



Case 2 - few measurements
```{r}
vital_sign_sample %>%
  filter(encounterId==1111) -> grouped_data2

grouped_data2$pr <- as.numeric(as.character(grouped_data2$pr))
grouped_data2$rr <- as.numeric(as.character(grouped_data2$rr))
grouped_data2$mBP <- as.numeric(as.character(grouped_data2$mBP))
grouped_data2$spO2 <- as.numeric(as.character(grouped_data2$spO2))


ggplot(data=grouped_data2, aes(x=time, y=value, color=variable)) + 
  geom_line(aes(y=pr, col="rr")) +
  geom_line(aes(y=rr, col="pr")) +
  geom_line(aes(y=spO2, col="spO2"))
```


The Patient arrived at:
```{r}
arrival_time2 <- encounter_sample$arrivalTime[encounter_sample$encounter_id==1111]
arrival_time2 <- na.omit(arrival_time)
arrival_time2
```


The patient was discharged at:
```{r}
discharge_time2 <- encounter_sample$discharge_time[encounter_sample$encounter_id==1111]
discharge_time2 <- na.omit(discharge_time)
discharge_time2
```


The patient was amitted for a total time of:
```{r}
difftime(discharge_time2, arrival_time2)
```


The patient have the total number of measurements
```{r}
grouped_data2 <- vital_sign_sample

grouped_data2 %>%
  group_by(encounterId) %>%
  mutate(number_of_measures=n()) -> grouped_data2
  
#Isolerer patient ID og tilhørende antal målinger
grouped_data2 %>%
  distinct(encounterId, number_of_measures) %>%
  arrange(desc(number_of_measures)) -> grouped_data2

grouped_data2$number_of_measures[grouped_data2$encounterId==53203607]
```



Case 3
- Gaps in measurements
```{r}
vital_sign_sample %>%
  filter(encounterId==1111) -> grouped_data3

grouped_data3$pr <- as.numeric(as.character(grouped_data3$pr))
grouped_data3$rr <- as.numeric(as.character(grouped_data3$rr))
grouped_data3$mBP <- as.numeric(as.character(grouped_data3$mBP))
grouped_data3$spO2 <- as.numeric(as.character(grouped_data3$spO2))


ggplot(data=grouped_data3, aes(x=time, y=value, color=variable)) + 
  geom_line(aes(y=pr, col="rr")) +
  geom_line(aes(y=rr, col="pr")) +
  geom_line(aes(y=spO2, col="spO2"))
```


The Patient arrived at:
```{r}
arrival_time3 <- encounter_sample$arrivalTime[encounter_sample$encounter_id==1111]
arrival_time3 <- na.omit(arrival_time)
arrival_time3
```


The patient was discharged at:
```{r}
discharge_time3 <- encounter_sample$discharge_time[encounter_sample$encounter_id==1111]
discharge_time3 <- na.omit(discharge_time)
discharge_time3
```


The patient was amitted for a total time of:
```{r}
difftime(discharge_time3, arrival_time3)
```


The patient have the total number of measurements
```{r}
grouped_data3 <- vital_sign_sample

grouped_data3 %>%
  group_by(encounterId) %>%
  mutate(number_of_measures=n()) -> grouped_data3
  
grouped_data3 %>%
  distinct(encounterId, number_of_measures) %>%
  arrange(desc(number_of_measures)) -> grouped_data3

grouped_data3$number_of_measures[grouped_data3$encounterId==53069837]
```
