---
title: "hetGP"
author: "Jens Hesel"
date: "30/3/2020"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Path to packages on OPEN
```{r}
.libPaths("P:/OP00904/R_pakker")
```

Loads packages
```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(readr)
library(ggplot2)
library(hetGP)
library(MASS)
library(xts)
library(tsbox)

```



///////////////////////////////////////////////////////////////////////////
Prepares data
//////////////////////////////////////////////////////////////////////////

Loads data
```{r}
vital_sign_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/vital_sign_final.csv")
encounter_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/encounterOverview.csv")
```



Selects patients
```{r}
id <- 1111

vital_sign_sample %>% 
  filter(encounterId==id) -> mydata
```


Makes vital signs numerical 
```{r}

mydata$pr <- as.numeric(as.character(mydata$pr))

```


Removes NULL values
```{r}
mydata %>%
  filter(!str_detect(pr, "NULL")) -> mydata
```


Plots PR according to time
```{r}
ggplot(aes(x=time, y=pr), data=mydata) + geom_line()
```


Selects control points
```{r}
con <- c("2018-06-13 20:04:33", "2018-06-14 00:26:33","2018-06-14 01:20:33","2018-06-14 06:21:32","2018-06-14 13:31:32" )


#case1 "2018-06-13 20:04:33", "2018-06-14 00:26:33","2018-06-14 01:20:33","2018-06-14 #06:21:32","2018-06-14 13:31:32"
#case2 "2018-06-15 15:51:30", "2018-06-15 16:01:30","2018-06-15 17:22:30","2018-06-15 #18:35:30","2018-06-15 20:36:30"
#case3 "2018-06-13 01:31:36", "2018-06-13 10:48:34","2018-06-13 12:52:34","2018-06-13 #14:50:34","2018-06-13 16:26:33"


mydf <- data.frame(con)
```



Checks wether it is POSIxct, has to be
```{r}
class(mydf$con)
```

Makes the data points POSIXct
```{r}
mydf$con <- as.POSIXct(as.factor(mydf$con))
```


Isolates pr and time
```{r}
mydata %>%
  distinct(pr, time) -> mydata2
```



Summary of the time of the patients stay
```{r}
summary(mydata2$time)
```


Divides data in test og train 
```{r}
set.seed(123) 
sample_size <- floor(0.55*nrow(mydata2))

sample <- sample(seq_len(nrow(mydata2)), size=sample_size)
train <- mydata2[sample,]
test <- mydata[-sample,]
```


Define the data that GPR is performed on
```{r}
work_data <- test
```


Define min and max used for normalization of time
```{r}
min <- as.numeric(min(mydata2$time))
max <- as.numeric(max(mydata2$time))
```


Normalize time needed for GPR
```{r}

work_data$num_time <- 0

for(i in 1:length(work_data$time)){
  
  current_time <- work_data$time[i]
  
  top <- as.numeric(current_time)-min
  bottom <- max-min
  
  num_time <- top/bottom
  
  work_data$num_time[i] <- num_time
  
  
  current_time <- 0
  num_time <- 0
}

```




Normalize timeinterval based on the control points
```{r}
conmatrix <- matrix(nrow = 5, ncol = 1)

for (i in 1:length(con)) {
  
  current <- mydf$con[i]
  
  tp <- as.numeric(current) - min
  bm <- max-min
  
  newtime <- tp/bm
  
  conmatrix[i,1] <- abs(newtime)
  
  current <- 0
  newtime <- 0
  
}
```





///////////////////////////////////////////////////////////////////////
GPR done using mleHetGP
///////////////////////////////////////////////////////////////////////

Sets seed for random number generator. 
```{r}
set.seed(32)
```

Initialize data and plots normalized time and pr 
```{r}
myx <- matrix(work_data$num_time, ncol=1)
myz <- work_data$pr
plot(myx, myz, ylim = c(20, 150), ylab = 'PR', xlab = "time")
```


Summary of rr
```{r}
summary(myz)
```


Makes the model for GPR
```{r}

settings <- list(return.hom = TRUE) # makes homoskedastic model used for training

model <- mleHetGP(X = myx, Z = myz,lower = 0.1, upper = 50,  covtype = "Matern5_2", settings = settings)


```


View of the fit from the model
```{r}
summary(model)
```


Plots the model
```{r}
plot(myx, myz, ylim = c(20, 150), ylab = 'PR', xlab = "time") #hollow points

# Create a prediction grid and obtain predictions
xgrid <- matrix(seq(0, 10, length.out = 500), ncol = 1)
predictions <- predict(x = xgrid, object = model)

# Display mean predictive surface
lines(xgrid, predictions$mean, col = 'red', lwd = 2)

# Display 95% confidence intervals, red dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)

# Display 95% prediction intervals, green dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)

```



Predicts values 
```{r}
gpr_data <- predict(object=model, x= conmatrix)
gpr_data
```






