---
title: "hetGP2"
author: "Jens Hesel"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Path to packages on OPEN
```{r}
.libPaths("P:/OP00904/R_pakker")
```

Loads packages
```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(readr)
library(ggplot2)
library(hetGP)
library(MASS)
library(xts)
library(tsbox)
```


///////////////////////////////////////////////////////////////////////////
Prepares data
//////////////////////////////////////////////////////////////////////////

Loads data
```{r}
vital_sign_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/vital_sign_final.csv")
encounter_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/encounterOverview.csv")
```



Selects patients
```{r}
id <- 1111

vital_sign_sample %>% 
  filter(encounterId==id) -> mydata

```

Makes vital signs numerical 
```{r}
mydata$pr <- as.numeric(as.character(mydata$pr))
```

Plots PR and time
```{r}
ggplot(aes(x=time, y=pr), data=mydata) + geom_line()
```

Isolates pr and time
```{r}
mydata %>%
  distinct(pr, time) -> mydata2
```


Selects start interval
case1 45:145
case2 18:38
case3 40:70
```{r}
starttime <- mydata2
startvalues <- starttime$pr[45:145]
starttime$pr[45:145] <- NA
startinterval <- starttime$time[45:145]
ggplot(aes(x=time, y=pr), data=starttime) + geom_line()
```


Selects middle interval
case1 300:400
case2 88:108
case3 170:200
```{r}
middletime <- mydata2
middlevalues <- middletime$pr[300:400]
middletime$pr[300:400] <- NA
middleinterval <- middletime$time[300:400]
ggplot(aes(x=time, y=pr), data=middletime) + geom_line()
```

Selects end interval
case1 800:900
case2 190:210
case3 330:360
```{r}
endtime <- mydata2
endvalues <- endtime$pr[800:900]
endtime$pr[800:900] <- NA
endinterval <- endtime$time[800:900]
ggplot(aes(x=time, y=pr), data=endtime) + geom_line()
```


Combined plot for illustration in the report
Selects start interval
case1 45:145
case2 18:38
case3 40:70
Selects middle interval
case1 300:400
case2 88:108
case3 170:200
Selects end interval
case1 800:900
case2 190:210
case3 330:360
```{r}
combined <- mydata2
combined$pr[224:226] <- NA
#Start
x1 <- as_datetime(c("2018-06-15 15:20:30"))
x2 <- as_datetime(c("2018-06-15 15:40:30"))
#middle
x3 <- as_datetime(c("2018-06-15 16:30:30"))
x4 <- as_datetime(c("2018-06-15 16:50:30"))
#end
x5 <- as_datetime(c("2018-06-15 18:10:30"))
x6 <- as_datetime(c("2018-06-15 18:28:30"))

ggplot(combined) + 
  geom_line(aes(x=time, y=pr)) +
  geom_vline(aes(xintercept = x1), linetype="dashed", color="red", size=1) +
  geom_vline(aes(xintercept = x2), linetype="dashed", color="red", size=1) +
  geom_vline(aes(xintercept = x3), linetype="dashed", color="blue", size=1) +
  geom_vline(aes(xintercept = x4), linetype="dashed", color="blue", size=1) +
  geom_vline(aes(xintercept = x5), linetype="dashed", color="green", size=1) +
  geom_vline(aes(xintercept = x6), linetype="dashed", color="green", size=1)

```


Gathers the intervals used for normalization
```{r}
mydf <- data.frame(startinterval, middleinterval, endinterval)
```


Define the data that GPR is performed on
```{r}
work_data <- starttime
```


Define min and max used for normalization of time
```{r}
min <- as.numeric(min(work_data$time))
max <- as.numeric(max(work_data$time))
```


Normalize time
Needed for GPR
```{r}

work_data$num_time <- 0

for(i in 1:length(work_data$time)){
  
  current_time <- work_data$time[i]
  
  top <- as.numeric(current_time)-min
  bottom <- max-min
  
  num_time <- top/bottom
  
  work_data$num_time[i] <- num_time
  
  
  current_time <- 0
  num_time <- 0
}

```




Normalize timeinterval based on the control points
REMEMBER TO CHANGE NB OF ROWS WHEN CASE CHANGE
```{r}

conmatrix <- matrix(nrow = 101, ncol = 1)

for (i in 1:length(startinterval)) {
  
  current <- mydf$startinterval[i]
  
  tp <- as.numeric(current) - min
  bm <- max-min
  
  newtime <- tp/bm
  
  conmatrix[i,1] <- abs(newtime)
  
  current <- 0
  newtime <- 0
  
}
```




///////////////////////////////////////////////////////////////////////
GPR done using mleHetGP
///////////////////////////////////////////////////////////////////////

Sets seed for random number generator. 
```{r}
set.seed(32)
```

Needed else mleHetGP wont work, NA values cant be in the matrix
```{r}
work_data <- na.omit(work_data)
```


Initialize data and plots normalized time and pr 
```{r}
myx <- matrix(work_data$num_time, ncol=1)
myz <- work_data$pr

plot(myx, myz, xlim = c(0, 0.4), ylim = c(30, 160), ylab = 'PR', xlab = "time")
```




Makes the model for GPR
```{r}
settings <- list(return.hom = TRUE) # makes homoskedastic model used for training

model <- mleHetGP(X = myx, Z = myz,lower = 0.1, upper = 50, covtype = "Matern5_2", settings = settings)
```


View of the fit from the model
```{r}
summary(model)
```

Plots the model
```{r}
plot(myx, myz, xlim = c(0, 0.4), ylim = c(30, 160), ylab = 'PR', xlab = "time") #hollow points

## Create a prediction grid and obtain predictions
xgrid <- matrix(seq(0, 10, length.out = 500), ncol = 1)
predictions <- predict(x = xgrid, object = model)

# Display mean predictive surface
lines(xgrid, predictions$mean, col = 'red', lwd = 2)

# Display 95% confidence intervals, red dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)

# Display 95% prediction intervals, green dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)

```

Predicts values 
```{r}
gpr_data <- predict(object=model, x= conmatrix)
gpr_data
```

Calculates the RMSE
REMEMBER TO CHANGE VALUES
```{r}
error <- gpr_data$mean - startvalues
error <- na.omit(error)
RMSE(error)
```

