---
title: "hetGP3"
author: "Jens Hesel"
date: "9/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Path to packages on OPEN
```{r}
.libPaths("P:/OP00904/R_pakker")
```

Loads packages
```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(readr)
library(ggplot2)
library(hetGP)
library(MASS)
library(xts)
library(tsbox)
```

Loads data
```{r}
vital_sign_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/vital_sign_final.csv")
encounter_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/encounterOverview.csv")
```


Selects patient
Works on case 2 
```{r}
id <- 1111

vital_sign_sample %>% 
  filter(encounterId==id) -> mydata
```

Makes vital signs numerical 
```{r}
mydata$pr <- as.numeric(as.character(mydata$pr))
```

Plots PR and time
```{r}
ggplot(aes(x=time, y=pr), data=mydata) + geom_line()
```

Isolates pr and time
```{r}
mydata %>%
  distinct(pr, time) -> mydata2

```

Removes the data around the interval 17:00-18:00
```{r}
testdata <- mydata2

testdata$pr[1:117] <- NA
testdata$pr[181:226] <- NA
testdata <- na.omit(testdata)
```

Overview
```{r}
summary(testdata)
```


Use 18:00 as controlpoint
```{r}
controlpoint <- testdata$pr[61]

#defines testdata, the point from 148 til start index
testdata$pr[41:61] <- NA

timeinterval <- testdata$time[1:61]
```


```{r}
mydf <- data.frame(timeinterval)
```


Define the data that GPR is performed on
```{r}
work_data <- testdata
```



Define min and max used for normalization of time
```{r}
min <- as.numeric(min(work_data$time))
max <- as.numeric(max(work_data$time))
```

Normalize time
Needed for GPR
```{r}

work_data$num_time <- 0

for(i in 1:length(work_data$time)){
  
  current_time <- work_data$time[i]
  
  top <- as.numeric(current_time)-min
  bottom <- max-min
  
  num_time <- top/bottom
  
  work_data$num_time[i] <- num_time
  
  
  current_time <- 0
  num_time <- 0
}

```

Normalize timeinterval based on the control points
REMEMBER TO CHANGE NB OF ROWS WHEN CASES CHANGE
```{r}

conmatrix <- matrix(nrow = 61, ncol = 1)

for (i in 1:length(timeinterval)) {
  
  current <- mydf$timeinterval[i]
  
  tp <- as.numeric(current) - min
  bm <- max-min
  
  newtime <- tp/bm
  
  conmatrix[i,1] <- abs(newtime)
  
  current <- 0
  newtime <- 0
  
}
```

///////////////////////////////////////////////////////////////////////
GPR done using mleHetGP
///////////////////////////////////////////////////////////////////////

Needed else mleHetGP wont work, NA values cant be in the matrix
```{r}
work_data <- na.omit(work_data)
```

Initialize data and plots normalized time and pr 
```{r}
myx <- matrix(work_data$num_time, ncol=1)
myz <- work_data$pr

plot(myx, myz, xlim = c(0,1), ylim = c(30, 130), ylab = 'pr', xlab = "time")
```





Makes the model for GPR
```{r}
settings <- list(return.hom = TRUE) # makes homoskedastic model used for training

model <- mleHetGP(X = myx, Z = myz,lower = 0.1, upper = 50, covtype = "Matern3_2", settings = settings)
```


View of the fit from the model
```{r}
summary(model)
```

Plots the model
```{r}
plot(myx, myz, xlim = c(0,1), ylim = c(60, 85), ylab = 'PR', xlab = "time") #hollow points

## Create a prediction grid and obtain predictions
xgrid <- matrix(seq(0, 10, length.out = 500), ncol = 1)
predictions <- predict(x = xgrid, object = model)

# Display mean predictive surface
lines(xgrid, predictions$mean, col = 'red', lwd = 2)

# Display 95% confidence intervals, red dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2)), col = 2, lty = 2)

# Display 95% prediction intervals, green dotted lines
lines(xgrid, qnorm(0.05, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)
lines(xgrid, qnorm(0.95, predictions$mean, sqrt(predictions$sd2 + predictions$nugs)),
col = 3, lty = 2)

```

Predicts value for control point, normalized so 1 = 18:00
```{r}
gpr_data <- predict(object=model, x= 1)
gpr_data
```
