---
title: "Data overall"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
.libPaths("P:/OP00904/R_pakker")
```


```{r}
library(tidyverse)
library(knitr)
library(lubridate)
library(xts)
library(tsbox)
library(readr)
```


```{r}
vital_sign_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/vital_sign_final.csv")
encounter_sample <- read_csv("//rsyd.net/appl$/_Shared/OUH/OpenAnalyze/ProjectData/OP00904/Jens/Data/encounterOverview.csv")
```




Number of patients in encounter sample
```{r}
length(encounter_sample$encounter_id)
```

Group by id and count number of measures
```{r}
vital_sign_sample %>%
  group_by(encounterId) %>%
  mutate(number_of_measures=n()) -> grouped_data
```

Removes duplicates of ID's
```{r}
grouped_data %>%
  distinct(encounterId, .keep_all = TRUE) -> grouped_data
```

Number of patients in Vital sign sample
```{r}
length(grouped_data$encounterId)
```


///////////////////////////////////////////////////////
Vital signs descriptive statistics
///////////////////////////////////////////////////////
```{r}
vital_sign_sample -> mydata

mydata %>%
  distinct(encounterId, mBP) -> mydata2

mydata2$mBP <- as.numeric(mydata2$mBP)
```

Removes NULL values
```{r}
mydata2 <- na.omit(mydata2)
```

Removes duplicates so each ID only once
```{r}
mydata2 %>%
  distinct(encounterId, .keep_all = TRUE) -> grouped_data2
```

Overview 
```{r}
summary(grouped_data2$mBP)
```

Overview of length of stay
```{r}
summary(abs(encounter_sample$length_of_stay_minutes))
```



////////////////////////////////////////////////////////////////////
Mean & Median
////////////////////////////////////////////////////////////////////
Makes length of stay numeric
```{r}
encounter_sample$length_of_stay_minutes <- as.numeric(encounter_sample$length_of_stay_minutes)
```

Selects patients admitted between 15 hours and 30 hours
```{r}
encounter_sample %>%
  filter(length_of_stay_minutes > 900) %>%
  filter(length_of_stay_minutes < 1800) -> timedata1
```

Select patients for group1 based on few measurements
```{r}
timedata1 %>%
  filter(m_load < 0.5) %>%
  filter(m_load > 0.1)-> group1
```

Selects patients for group2 based on many measures
```{r}
timedata1 %>%
  filter(m_load > 0.5) -> group2
```


Initialize dataframe and values
```{r}
dfID1 <- group1$encounter_id #change for group2
mylength <- length(dfID1)
mydf <- data.frame(matrix(nrow = length(dfID1), ncol = 3))
names(mydf)[1] <- "Id"
names(mydf)[2] <- "RMSEmean"
names(mydf)[3] <- "RMSEmedian"

```

Prepares data
```{r}
vital_sign_sample -> loaded_data

loaded_data$spO2 <- as.numeric(loaded_data$spO2)
loaded_data$rr <- as.numeric(loaded_data$rr)
loaded_data$pr <- as.numeric(loaded_data$pr)

loaded_data %>%
  filter(!str_detect(spO2, "NULL")) -> loaded_data #current vital sign
```



Calculates RMSE all patients in the group
```{r}
mycounter <- 0

for (i in 1:mylength) {
  
  plusplus(mycounter)
  id <- dfID1[i]
  
  currentid <- id

loaded_data %>%
  filter(encounterId==currentid) -> data

require(xts)
raw_data <- xts(data$spO2, as.POSIXct(data$time, 
                                              format="%d/%m/%Y %H:%M:%S"))

if (length(raw_data)==0) {next}
else{

raw_data <- na.omit(raw_data)

#Calculates mean and median
ep <- endpoints(raw_data, on = "hours", k=1)
mean <- period.apply(raw_data, INDEX = ep, FUN = mean)
median <- period.apply(raw_data, INDEX = ep, FUN = median)

#Calculates differences
diffmean <- raw_data - mean
diffmean <- as.numeric(diffmean)
diffmean <- abs(diffmean)
diffmedian <- raw_data - median
diffmedian <- as.numeric(diffmedian)
diffmedian <- abs(diffmedian)

#calculates RMSE
RMSEmean <- RMSE(diffmean)
RMSEmedian <- RMSE(diffmedian)

#Puts data into dataframe
mydf$Id[mycounter] <- currentid
mydf$RMSEmean[mycounter] <- RMSEmean
mydf$RMSEmedian[mycounter] <- RMSEmedian
}
}
```

Calculates overall RMSE for mean
```{r}
mytest <- na.omit(mydf)

mean(mytest$RMSEmean)
```

Calculates overall RMSE for median
```{r}
mean(mytest$RMSEmedian)
```

